A Fast kNN Algorithm Using Multiple Space-Filling Curves

### 2022-05-23 2022/Sensors/kNN.tex
revised paper submitted

\textcolor[rgb]{1,0,0}{The maximum number of simultaneous mappings in the set $Y_L(x)$ from (\ref{EvSet}) will also be determined by the accuracy of the input data, which affects the accuracy of constructing the evolvents $y^i(x)$.
Let us assume that each of the mappings  $y^i(x)$ is constructed using the same value of $M$. Then the value of $L$ must satisfy the inequality $L \leq M$. Otherwise the points $y' = y^l(x'),\; y''=y^l(x'')$ from condition (\ref{y_prime}) will correspond to the centre of the same subcube with $p>M$, i.e. the equality  $y' = y''$ will be fulfilled, leading to violation of the conditions of Theorem 1.}

@@

%Штанюк
\begin{figure}
\widefigure
\includegraphics[width=0.5\linewidth]{figW.pdf}
\caption{\textcolor[rgb]{1,0,0}{Running times of the algorithms with $N = 3$, 7 million objects}\label{figW}}
\end{figure}

>>>>

\textcolor[rgb]{1,0,0}{The maximum number of simultaneous mappings in the set $Y_L(x)$ from (\ref{EvSet}) will also be determined by the accuracy of the input data, which affects the accuracy of constructing the evolvents $y^i(x)$.
Let us assume that each of the mappings  $y^i(x)$ is constructed using the same value of $M$. Then the value of $L$ must satisfy the inequality $L < M$. Otherwise the points $y' = y^l(x'),\; y''=y^l(x'')$ from condition (\ref{y_prime}) will correspond to the centre of the same subcube with $p \geq M$, i.e. the equality  $y' = y''$ will be fulfilled, leading to violation of the conditions of Theorem 1.}

@@

%Штанюк
\begin{figure}
\widefigure
\includegraphics[width=0.5\linewidth]{figW.pdf}
\caption{Running times of the algorithms with $N = 3$, 7 million objects\label{figW}}
\end{figure}
